\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../diagrams/}}}
\begin{document}

To show that application works properly, there will be described some steps to perform activities and check if they matches expected outcome. 


\subsection{Client making the order on the web app}

\begin{enumerate}
    
    \item Client logs into the web app.
    \item The list of available products with prices shows up.
    \item Client can filter and sort products.
    \item Client adds some products to shopping cart and chooses product quantity in a modal box.
    \item Client chooses the payment method and submits the order.
    \item Client module informs the shop module, that there is a new pending order.
    \item Client module informs the delivery module, that there is a new pending order.
    \item Shop worker gets notification and accepts pending order.
    \item Courier gets notification and accepts pending order.
    \item Shop worker notifies the courier, that the package is ready.
    \item Courier receive the package and delivers it to the client.
    \item Client is notified, when the courier is at a given location.


\end{enumerate}



\subsection{Shop manager adding new product on the web app}

\begin{enumerate}
    \item Shop manager logs into the web app.
    \item The list of products offer shows up.
    \item Shop manager clicks the "Add new product" button.
    \item The modal box with appropriate text inputs shows up.
    \item Shop manager fills required fields and attaches the picture.
    \item The new product is visible in the products list.
\end{enumerate}

\subsection{Shop worker is preparing an order}

\begin{enumerate}
    \item Shop worker starts working by logging in
    \item After successful logging he should be declared as available
    \item He can check if there are pending orders, if so he choose one and start collecting in
    \item He should now have options to abandon the order or accept collecting while sending notification to courier
    \item Shop worker can log off
\end{enumerate}

\subsection{Making a complaint}

\begin{enumerate}
    \item Client makes a complaint after receiving an order
    \item Client can add or delete highlighted products which did not meet his expectations
    \item Client can submit a complaint
    \item Shop worker can see list of complained products
    \item Shop worker can mark which products are right justified to complain
    \item Shop worker can see amount of money he need to recharge to a client
    \item Shop worker can send appropriate amount of money to a client
\end{enumerate}


\end{document}